### 2013-05-26 menger.tex
Fixed sorgenfrey typos
edited some menger stuff

  \begin{example}
    $F \kmarkwin{2} \mengame{\oneptlind{\omega_1}}$
  \end{example}

  \begin{proof}
    Using the functions $f_\alpha$ from the previous lemma, let \[\tau(\alpha_n,\alpha_{n+1},n+1)=f_{\alpha_n}^{-1}([0,n]) \cup \{\beta<\alpha_n,\alpha_{n+1} : f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)\}\]

    For any sequence $\alpha_n$, suppose that $\beta<\alpha_n$ for all $n$, and $\beta$ is not covered by \[\{\tau(\alpha_n,\alpha_{n+1},n+1): n<\omega\}\] Then we see first that $f_{\alpha_n}(\beta)=f_{\alpha_{n+1}}(\beta)$ for all $n$. However, $f_{n}(\beta)>n$ for all $n$ as well, which is a contradiction.

    Finally, for each open cover $\mc{U}$, assign arbirtary $\alpha(\mc{U})$, $U(\mc{U})$ such that $[\alpha(\mc{U}),\omega_1)\cup\{\infty\}$ is a subset of $U(\mc{U})\in\mc{U}$. Then a $2$-Markov strategy $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ which chooses $U(\mc{U}_n)$ and covers the finite set $\tau(\alpha(\mc{U}_n),\alpha(\mc{U}_{n+1}),n+1)$ is a winning strategy for $F$.
  \end{proof}

@@

>>>>

@@

  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.

  \begin{definition}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a fuction $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

  Obviously $\sigma$-compact implies \scish implies Lindel\"of. We shall see that the non-$\sigma$-compact space $\omega_1^\dagger$ is \scish.

  \begin{theorem}
    The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
  \end{theorem}

  \begin{proof}
    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha\rest\beta =^* f_\beta$. Let $\gamma(\mc U)$ identify the least ordinal such that $[\gamma(\mc U),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$. Then $f(\mc U,n)=f^{-1}_{\gamma(\mc U)}([0,n]) \cup [\gamma(\mc U),\omega_1)\cup\{\infty\}$ is easily seen to witness the property.
  \end{proof}

  \begin{theorem}
    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
  \end{theorem}

  \begin{proof}
    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$. So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m< N$, $x \in f(\mc{U}_m,N)\setminus (f(\mc{U}_{m},N-1)\cup f(\mc{U}_{m+1},N))$ and is covered by the strategy during round $m+1$.
  \end{proof}

  \begin{corollary}
    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
  \end{corollary}
